3.7: Regression with Interaction Effects - R Practice

### 2019-11-14 static/r/19-r-practice-rmd.Rmd
Add class 19 content

---
title: "3.7: Regression with Interaction Effects - R Practice"
editor_options: 
  chunk_output_type: console
---

```{r message=FALSE, warning=FALSE, include=FALSE}
library(tidyverse)
library(pander)
source(file.path(here::here(), "lib", "graphics.R"))
```

@@

@@

## Question 6

Let's recode the sex variable.

Make a new variable called `Male` and save it in your dataframe.^[Hint: `mutate()` and define `Male` equal to the `ifelse()` function, which has three arguments: 1. the condition to test, 2. what to define "Male" as when the condition is `TRUE`, and 3. what to define "Male" as when the condition is `FALSE`.]

Run the same regression as in question 5, but use `Male` instead of `Female`.

@@

Now let's see if the difference in fine between men and women are different depending on the driver's age. Run the regression again, but add an **interaction term** between `Female` and `Age` interaction term.

Write out your estimated regression equation.

Interpret the interaction effect. Is it statistically significant?

Plugging in 0 or 1 as necessary, rewrite (on your paper) this regression as *two separate* equations, one for Males and one for Females.

@@

@@

What does each coefficient mean?

Using the regression equation, what are the means for

@@

>>>>

---
title: "3.7: Regression with Interaction Effects - R Practice"
author: "YOUR NAME"
date: "`r Sys.Date()`"
output:
  html_document:
    df_print: paged
    #theme: 
    toc: true 
    toc_depth: 3
    toc_float: true
    code_folding: show
    highlight: tango
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

@@

---

<!--ANSWER BELOW HERE-->

```{r}
# PUT CODE HERE
```

---

### Part A
Write out the estimated regression equation.

---

<!--ANSWER BELOW HERE-->

```{r}
# PUT CODE HERE
```

---

### Part B
Use the regression coefficients to find

@@

---

<!--ANSWER BELOW HERE-->

```{r}
# PUT CODE HERE
```

---

## Question 6
Let's recode the sex variable.

### Part A
Make a new variable called `Male` and save it in your dataframe.^[Hint: `mutate()` and define `Male` equal to the `ifelse()` function, which has three arguments: 1. the condition to test, 2. what to define "Male" as when the condition is `TRUE`, and 3. what to define "Male" as when the condition is `FALSE`.]

---

<!--ANSWER BELOW HERE-->

```{r}
# PUT CODE HERE
```

---

### Part B
Run the same regression as in question 5, but use `Male` instead of `Female`.

---

<!--ANSWER BELOW HERE-->

```{r}
# PUT CODE HERE
```

---

### Part C
Write out the estimated regression equation.

---

<!--ANSWER BELOW HERE-->

```{r}
# PUT CODE HERE
```

---

@@

---

<!--ANSWER BELOW HERE-->

```{r}
# PUT CODE HERE
```

---

### Part B
Now let's see if the difference in fine between men and women are different depending on the driver's age. Run the regression again, but add an **interaction term** between `Female` and `Age` interaction term.

---

<!--ANSWER BELOW HERE-->

```{r}
# PUT CODE HERE
```

---

### Part C
Write out your estimated regression equation.

---

<!--ANSWER BELOW HERE-->

```{r}
# PUT CODE HERE
```

---

### Part D
Interpret the interaction effect. Is it statistically significant?

---

<!--ANSWER BELOW HERE-->

```{r}
# PUT CODE HERE
```

---

### Part E
Plugging in 0 or 1 as necessary, rewrite (on your paper) this regression as *two separate* equations, one for Males and one for Females.

---

<!--ANSWER BELOW HERE-->

```{r}
# PUT CODE HERE
```

---

@@

---

<!--ANSWER BELOW HERE-->

```{r}
# PUT CODE HERE
```

----

@@

---

<!--ANSWER BELOW HERE-->

```{r}
# PUT CODE HERE
```

---

### Part D
What does each coefficient mean?

---

<!--ANSWER BELOW HERE-->

```{r}
# PUT CODE HERE
```

---

### Part E
Using the regression equation, what are the means for

@@

---

<!--ANSWER BELOW HERE-->

```{r}
# PUT CODE HERE
```
